Computing Entropies With Nested Sampling

### 2017-06-07 paper/ms.tex
Some writing about NS

Nested Sampling \citep[NS][]{skilling2006nested} is an algorithm whose aim is
to calculate the evidence
\begin{align}
Z &= \int \pi(\x) L(\x) \, d\x
\end{align}
where $\x$ is the unknown parameter(s), $\pi$ is the prior distribution,
and $L$ is the likelihood function. It does this evolving a population of
$N$ particles in the parameter space.
Defining $X(\ell)$ as the amount of prior mass with likelihood greater than
some threshold $\ell$,
\begin{align}
X(\ell) &= \int \pi(\x) \mathds{1}\left(L(\x) > \ell\right) \, d\x,
\end{align}

The $N$ particles are initially initialised from the prior $\pi(\x)$, and the
particle with the lowest likelihood is found.
{\todo Write more here}

@@

The entropy of this question is
\begin{align}
H(Q) &= f_{1,2,3}\\
     & \quad \quad + \left(f_{2,3,4} - f_{2,3}\right) \\
     & \quad \quad + \left(f_{3,4,5} - f_{3,4}\right) \\
     & \quad \quad + ... \\
     & \quad \quad + \left(f_{8,9,10} - f_{8,9}\right).
\end{align}

>>>>

Nested Sampling \citep[NS][]{skilling2006nested} is an algorithm whose aim is
to calculate the evidence
\begin{align}
Z &= \int \pi(\x) L(\x) \, d\x
\end{align}
where $\x$ is the unknown parameter(s), $\pi$ is the prior distribution,
and $L$ is the likelihood function. It does this evolving a population of
$N$ particles in the parameter space.
The $N$ particles are initially initialised from the prior $\pi(\x)$, and the
particle with the lowest likelihood, $L^*_1$, is found and its details are
recorded in the output. This worst particle is then discarded
and replaced by a new particle
drawn from the prior $\pi$ but subject to the constraint that its likelihood
must be above $L^*_1$. This process is repeated, resulting in an
increasing sequence of likelihoods
\begin{align}
L^*_1, L^*_2, L^*_3..., 
\end{align}

Defining $X(\ell)$ as the amount of prior mass with likelihood greater than
some threshold $\ell$,
\begin{align}
X(\ell) &= \int \pi(\x) \mathds{1}\left(L(\x) > \ell\right) \, d\x,
\end{align}
\citet{skilling}'s key insight was that we can estimate the corresponding
$X$-values of the discarded points can be estimated from the nature of the
algorithm. Specifically, each iteration reduces the prior mass by approximately
a factor $e^{-1/N}$. More accurately, the conditional distribution of
$X_{i}$ given $X_{i-1}$ (and the definition of the algorithm)
is obtainable by letting
$t_i \sim \textnormal{Beta}(N,1)$ and setting $X_{i+1} := t_iX_{i-1}$.

@@

The entropy of this question is
\begin{align}
H(Q) &= h_{1,2,3}\\
     & \quad \quad + \left(h_{2,3,4} - h_{2,3}\right) \\
     & \quad \quad + \left(h_{3,4,5} - h_{3,4}\right) \\
     & \quad \quad + ... \\
     & \quad \quad + \left(h_{8,9,10} - h_{8,9}\right).
\end{align}
where $h_{x} = -P(x)\log P(x)$.
